---
title: "Frequentist Base Analysis"
author: "Anwesha Guha"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(here, rio, tidyverse)
```

```{r}
load(here("data", "combined_clean.RData"))
```

## R Markdown

```{r create_dat}
dat <- full %>% 
  select(-contains("weight")) %>% 
  mutate(across(c(id, region, race_ethnicity, sex, age), as.factor)) %>% 
  select(
    id,             # ID
    wave,           # wave
    region, race_ethnicity, sex, age,  # strata
    eprod_edsd      # outcome
  )
#64,623 observations

dat_na <-  dat %>% 
  filter(if_any(everything(), is.na))

dat <- dat %>% 
 drop_na()

dat <- dat %>% 
 mutate(strata_label = as.factor(paste(region, race_ethnicity, sex, age, sep = "_")))
```

```{r strata_by_outcome}
dat %>% 
 group_by(strata_label) %>% 
 summarize(tot = sum(eprod_edsd)) %>% 
 arrange(tot)
```

```{r separate_waves}
dat_4 <- dat %>% 
 filter(wave == 4)

dat_7 <- dat %>% 
 filter(wave == 7)
```

## Null model

### Wave 4
```{r}
library(lme4)

mod1_4 <- glmer(eprod_edsd ~ (1 | strata_label), 
               data = dat_4,
               family = binomial(link = "logit"))

summary(mod1_4)

# Predict the fitted linear predictor (on the probability scale)
dat_4$mod1xbu <- predict(mod1_4, type = "response")

# Predict the linear predictor for the fixed portion of the model only
# (only the intercept, so this is just the weighted grand mean probability)
dat_4$mod1xb <- predict(mod1_4, type="response", re.form=NA)
```

### Wave 7
```{r}
mod1_7 <- glmer(eprod_edsd ~ (1 | strata_label), 
               data = dat_7,
               family = binomial(link = "logit"))

summary(mod1_7)

# Predict the fitted linear predictor (on the probability scale)
dat_7$mod1xbu <- predict(mod1_7, type = "response")

# Predict the linear predictor for the fixed portion of the model only
# (only the intercept, so this is just the weighted grand mean probability)
dat_7$mod1xb <- predict(mod1_7, type="response", re.form=NA)
```

## Additive model

### Wave 4
```{r}
library(merTools)

mod2_4 <- glmer(eprod_edsd ~ region + race_ethnicity + sex + age + (1 | strata_label),
                data = dat_4,
                family = binomial(link = "logit")) #change reference to White, Male, 18-24, Northeast or West

summary(mod2_4)

# Predict the fitted linear predictor (on the probability scale)
dat_4$mod2m <- predict(mod2_4, type = "response")


# predict the fitted linear predictor, and confidence intervals, on the logit 
# scale
m2m_4 <- predictInterval(mod2_4, level=0.95, include.resid.var=FALSE)
# create a new id variable for this newly created dataframe
m2m_4 <- mutate(m2m_4, id=row_number())
# on the logit scale, predict the linear predictor for the fixed portion of the
# model only
dat_4$m2mF <- predict(mod2_4, re.form=NA)

# predict the fitted linear predictor, and confidence intervals, on the 
# probability scale
m2m_prob_4 <- predictInterval(mod2_4, level=0.95, include.resid.var=FALSE, 
                             type="probability") 
# note that, unlike the stata code, this code combines the uncertainty from the
# fixed and random parts. This saves a step later compared to the Stata code.

# create a new id variable for this newly created dataframe
m2m_prob_4 <- mutate(m2m_prob_4, id=row_number())

# predict the fitted linear predictor, on the probability scale, for the fixed 
# portion of the model only
dat_4$m2xb <- predict(mod2_4, re.form=NA, type="response")

#predict the stratum random effects and associated standard errors
m2u_4 <- REsim(mod2_4)
```

### Wave 7

```{r}
mod2_7 <- glmer(eprod_edsd ~ region + race_ethnicity + sex + age + (1 | strata_label),
                data = dat_7,
                family = binomial(link = "logit"))

summary(mod2_7)

# Predict the fitted linear predictor (on the probability scale)
dat_7$mod2m <- predict(mod2_7, type = "response")


# predict the fitted linear predictor, and confidence intervals, on the logit 
# scale
m2m_7 <- predictInterval(mod2_7, level=0.95, include.resid.var=FALSE)
# create a new id variable for this newly created dataframe
m2m_7 <- mutate(m2m_7, id=row_number())

# on the logit scale, predict the linear predictor for the fixed portion of the
# model only
dat_7$m2mF <- predict(mod2_7, re.form=NA)

# predict the fitted linear predictor, and confidence intervals, on the 
# probability scale
m2m_prob_7 <- predictInterval(mod2_7, level=0.95, include.resid.var=FALSE, 
                             type="probability") 
# note that, unlike the stata code, this code combines the uncertainty from the
# fixed and random parts. This saves a step later compared to the Stata code.

# create a new id variable for this newly created dataframe
m2m_prob_7 <- mutate(m2m_prob_7, id=row_number())

# predict the fitted linear predictor, on the probability scale, for the fixed 
# portion of the model only
dat_7$m2xb <- predict(mod2_7, re.form=NA, type="response")

#predict the stratum random effects and associated standard errors
m2u_7 <- REsim(mod2_7)
```

## Model diagnostics

### Wave 4

PCV
```{r}
vc1a <-as.data.frame(VarCorr(mod1_4))
vc1b <-as.data.frame(VarCorr(mod2_4))

PCV1 <- ((vc1a[1,4] - vc1b[1,4]) / vc1a[1,4])*100
PCV1 
```

AUCs
```{r}
library(Metrics)
## Wave 4

# Calculate the area under the receiver operating characteristic (ROC) curve
# for model 2a - based on intercept and stratum random effects
AUC2A <- auc(dat_4$eprod_edsd, dat_4$mod1xbu)

#for model 2A - based on only the fixed portion of the model
AUC2AF <- auc(dat_4$eprod_edsd, dat_4$mod1xb)

#for model 2b - based on intercept, main effects, and stratum random effects
AUC2B <- auc(dat_4$eprod_edsd, dat_4$m2mF)
#for model 2b - based on the fixed portion of the model (main effects)
AUC2BF <- auc(dat_4$eprod_edsd, dat_4$m2xb) 

#output the AUC calculations
AUC2A
AUC2AF
AUC2B
AUC2BF
```

### Wave 7

PCV
```{r}
vc1a <-as.data.frame(VarCorr(mod1_7))
vc1b <-as.data.frame(VarCorr(mod2_7))

PCV1 <- ((vc1a[1,4] - vc1b[1,4]) / vc1a[1,4])*100
PCV1 
```

AUCs
```{r}
library(Metrics)
## Wave 7

# Calculate the area under the receiver operating characteristic (ROC) curve
# for model 2a - based on intercept and stratum random effects
AUC2A <- auc(dat_7$eprod_edsd, dat_7$mod1xbu)

#for model 2A - based on only the fixed portion of the model
AUC2AF <- auc(dat_7$eprod_edsd, dat_7$mod1xb)

#for model 2b - based on intercept, main effects, and stratum random effects
AUC2B <- auc(dat_7$eprod_edsd, dat_7$m2mF)
#for model 2b - based on the fixed portion of the model (main effects)
AUC2BF <- auc(dat_7$eprod_edsd, dat_7$m2xb) 

#output the AUC calculations
AUC2A
AUC2AF
AUC2B
AUC2BF
```

## Visualizations

### Histograms

#### Wave 4

```{r}
# Histogram of the observed stratum means (and mean of means)
dat_4 %>% 
 group_by(strata_label) %>% 
 summarise(avg = mean(eprod_edsd)) %>% 
 ggplot(., aes(avg)) +
 geom_histogram(fill = "gray") +
  labs(title = "Observed Eproduct Use",
       x = "Observed Eprod Use",
       y = "Percent of Strata") +
 geom_vline(aes(xintercept = mean(avg))) +
 theme_minimal()


# Histogram of the predicted stratum means
ggplot(dat_4, aes(x=mod1xbu)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), fill = "gray") + 
  scale_y_continuous(labels=scales::percent) +
  labs(title = "Predicted Eproduct Use",
       x = "Predicted Eprod Use",
       y = "Percent of Strata") +
  geom_vline(aes(xintercept=0.07551613))+ #this is the precision weighted grand mean
  theme_minimal()
```

#### Wave 7

```{r}
# Histogram of the observed stratum means (and mean of means)
dat_7 %>% 
 group_by(strata_label) %>% 
 summarise(avg = mean(eprod_edsd)) %>% 
 ggplot(., aes(avg)) +
 geom_histogram(fill = "gray") +
  labs(title = "Observed Eproduct Use",
       x = "Observed Eprod Use",
       y = "Percent of Strata") +
 geom_vline(aes(xintercept = mean(avg))) +
 theme_minimal()


# Histogram of the predicted stratum means
ggplot(dat_7, aes(x=mod1xbu)) + 
  geom_histogram(aes(y = after_stat(count / sum(count))), fill = "gray") + 
  scale_y_continuous(labels=scales::percent) +
  labs(title = "Predicted Eproduct Use",
       x = "Predicted Eprod Use",
       y = "Percent of Strata") +
  geom_vline(aes(xintercept=0.1071728))+ #this is the precision weighted grand mean
  theme_minimal()
```

### Ranks

```{r}
###################################
# create a data frame at the strata level (with the means of each variable)
##################################

# first, merge predictions with original data

# create an id variable for merging in the tut dataframe
dat_4$id <- seq.int(nrow(dat_4))

# merge in m2bm_prob
dat_4 <- merge(dat_4, m2m_prob_4, by="id")

dat_4 <- dat_4 %>%
  rename(
    m2mfit=fit,
    m2mupr= upr,
    m2mlwr=lwr
  )

# merge in m2Bm
dat_4 <- merge(dat_4, m2m_4, by="id")

dat_4 <- dat_4 %>%
  rename(
    m2mfitL=fit,
    m2muprL= upr,
    m2mlwrL=lwr
  )

dat_4 <- dat_4 %>%
  group_by(strata_label) %>%
  mutate(strataN = n())
 

# Collapse the data down to a stratum-level dataset 
stratum_level <- aggregate(x=dat_4["eprod_edsd"], 
                  by=dat_4[c("region", "age", "sex", "race_ethnicity",
                  "strata_label", "strataN",
                  "m2mfit", "m2mupr", "m2mlwr", 
                  "m2mfitL", "m2muprL", "m2mlwrL",
                  "m2mF")],
                  FUN=mean)

stratum_level <- aggregate(x=dat_4[c("eprod_edsd", "m2mfit", "m2mupr", "m2mlwr", 
                  "m2mfitL", "m2muprL", "m2mlwrL",
                  "m2mF")], 
                  by=dat_4[c("region", "age", "sex", "race_ethnicity",
                  "strata_label", "strataN")],
                  FUN=mean)

# convert the outcome from a proportion to a percentage
stratum_level$eprod_edsd <- stratum_level$eprod_edsd*100
```

```{r}
###################################
# create a data frame at the strata level (with the means of each variable)
##################################

# first, merge predictions with original data

# create an id variable for merging in the tut dataframe
dat_7$id <- seq.int(nrow(dat_7))

# merge in m2bm_prob
dat_7 <- merge(dat_7, m2m_prob_7, by="id")

dat_7 <- dat_7 %>%
  rename(
    m2mfit=fit,
    m2mupr= upr,
    m2mlwr=lwr
  )

# merge in m2Bm
dat_7 <- merge(dat_7, m2m_7, by="id")

dat_7 <- dat_7 %>%
  rename(
    m2mfitL=fit,
    m2muprL= upr,
    m2mlwrL=lwr
  )

dat_7 <- dat_7 %>%
  group_by(strata_label) %>%
  mutate(strataN = n())
 

# Collapse the data down to a stratum-level dataset 
stratum_level_7 <- aggregate(x=dat_7["eprod_edsd"], 
                  by=dat_7[c("region", "age", "sex", "race_ethnicity",
                  "strata_label", "strataN",
                  "m2mfit", "m2mupr", "m2mlwr", 
                  "m2mfitL", "m2muprL", "m2mlwrL",
                  "m2mF")],
                  FUN=mean)

stratum_level_7 <- aggregate(x=dat_7[c("eprod_edsd", "m2mfit", "m2mupr", "m2mlwr", 
                  "m2mfitL", "m2muprL", "m2mlwrL",
                  "m2mF")], 
                  by=dat_7[c("region", "age", "sex", "race_ethnicity",
                  "strata_label", "strataN")],
                  FUN=mean)

# convert the outcome from a proportion to a percentage
stratum_level_7$eprod_edsd <- stratum_level_7$eprod_edsd*100
```

#### Wave 4

```{r}

# Rank the predicted stratum probabilities
stratum_level <- stratum_level %>%
  mutate(rank2=rank(m2mfit))

# convert probabilities to percentages
stratum_level$m2mfit <- stratum_level$m2mfit * 100
stratum_level$m2mupr <- stratum_level$m2mupr * 100
stratum_level$m2mlwr <- stratum_level$m2mlwr * 100

# Plot the caterpillar plot of the predicted stratum means
plot_4 <- ggplot(stratum_level, aes(y=m2mfit, x=rank2)) +
  geom_point() +
  geom_pointrange(aes(ymin=m2mlwr, ymax=m2mupr)) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Wave 4") +
  xlab("Stratum Rank") + 
  theme_bw()

# Generate list of 6 highest and 6 lowest predicted stratum means (for Table 4)
stratum_level <- stratum_level[order(stratum_level$rank2),]
head(stratum_level)
tail(stratum_level)

ranks <- stratum_level %>% 
 dplyr::select(region, age, sex, race_ethnicity, strata_label, strataN, eprod_edsd, m2mfit, rank2) %>% 
 arrange(-rank2)

ranks
```

#### Wave 7
```{r}
# Rank the predicted stratum probabilities
stratum_level_7 <- stratum_level_7 %>%
  mutate(rank2=rank(m2mfit))

# convert probabilities to percentages
stratum_level_7$m2mfit <- stratum_level_7$m2mfit * 100
stratum_level_7$m2mupr <- stratum_level_7$m2mupr * 100
stratum_level_7$m2mlwr <- stratum_level_7$m2mlwr * 100

# Plot the caterpillar plot of the predicted stratum means
plot_7 <- ggplot(stratum_level_7, aes(y=m2mfit, x=rank2)) +
  geom_point() +
  geom_pointrange(aes(ymin=m2mlwr, ymax=m2mupr)) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Wave 4") +
  xlab("Stratum Rank") + 
  theme_bw()

# Generate list of 6 highest and 6 lowest predicted stratum means (for Table 4)
stratum_level_7 <- stratum_level_7[order(stratum_level_7$rank2),]
head(stratum_level_7)
tail(stratum_level_7)

ranks <- stratum_level_7 %>% 
 dplyr::select(region, age, sex, race_ethnicity, strata_label, strataN, eprod_edsd, m2mfit, rank2) %>% 
 arrange(-rank2)

ranks
```

#### Both waves
```{r}
stratum_level$wave <- 4
stratum_level_7$wave <- 7

plot_dat <- bind_rows(stratum_level, stratum_level_7)
```

```{r}
plot_4 <- plot_dat %>% 
 filter(wave == 4) %>% 
 mutate(strata_label = str_replace_all(strata_label, "_", " ")) %>% 
 ggplot(aes(y = m2mfit, x = reorder(strata_label, m2mfit))) +
  geom_pointrange(aes(ymin = m2mlwr, ymax = m2mupr)) +
  geom_point(color = "orange", alpha = 0.7) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Wave 4") +
  xlab("Strata") +
 labs(title = "Wave 4 Predicted Percent EDSD E-Product Usage") +
  coord_flip() +
  theme_bw()

plot_7 <- plot_dat %>% 
 filter(wave == 7) %>% 
 mutate(strata_label = str_replace_all(strata_label, "_", " ")) %>% 
 ggplot(aes(y = m2mfit, x = reorder(strata_label, m2mfit))) +
  geom_pointrange(aes(ymin = m2mlwr, ymax = m2mupr)) +
  geom_point(color = "magenta", alpha = 0.7) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Wave 7") +
  xlab("Strata") +
  labs(title = "Wave 7 Predicted Percent EDSD E-Product Usage") +
  coord_flip() +
  theme_bw()
```

```{r}
plot_both <- ggplot(
  plot_dat %>%
    filter(wave %in% c(4, 7)) %>%
    group_by(strata_label) %>%
    mutate(diff = m2mfit[wave == 7] - m2mfit[wave == 4]) %>%
    ungroup() %>%
    mutate(strata_label = reorder(strata_label, diff)),
  aes(y = m2mfit, x = strata_label)
) +
  geom_pointrange(aes(ymin = m2mlwr, ymax = m2mupr)) +
  geom_point(aes(color = as.factor(wave))) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Both Waves") +
  xlab("Strata") +
  coord_flip() +
  labs(color = "Wave",
       title = "Predicted E-Product Usage by Strata, \nOrdered by Largest Difference between Waves") +
  theme_bw() +
  theme(
    legend.position = c(0.95, 0.05),
    legend.justification = c("right", "bottom")
  )
```

```{r}
# I know there is a better way to do this, but it was taking me too much time so I am manually pulling the strata names

top15_strata <- plot_dat %>%
  filter(wave %in% c(4, 7)) %>%
  dplyr::select(strata_label, wave, m2mfit) %>%
  pivot_wider(names_from = wave, values_from = m2mfit, names_prefix = "wave_") %>%
  mutate(diff = wave_7 - wave_4,
         strata_label = str_replace_all(strata_label, "_", " ")) %>%
  arrange(desc(diff)) %>%
  slice_head(n = 15) %>%
  pull(strata_label)



top15_plot <- ggplot(
  plot_dat %>%
    filter(wave %in% c(4, 7)) %>%
    group_by(strata_label) %>%
    mutate(diff = m2mfit[wave == 7] - m2mfit[wave == 4],
           strata_label = str_replace_all(strata_label, "_", " ")) %>%
    ungroup() %>%
    mutate(strata_label = reorder(strata_label, diff)) %>% 
   filter(strata_label %in% top15_strata),
  aes(y = m2mfit, x = strata_label)
) +
  geom_pointrange(aes(ymin = m2mlwr, ymax = m2mupr)) +
  geom_point(aes(color = as.factor(wave)), size = 4, alpha = 0.7) +
  ylab("Predicted Percent EDSD E-Product User, Model 2 for Both Waves") +
  xlab("Strata") +
  coord_flip() +
  labs(color = "Wave",
       title = "Strata with Largest Differences between Wave 4 and Wave 7") +
  theme_bw() +
  theme(
    legend.position = c(0.95, 0.05),
    legend.justification = c("right", "bottom"),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.y = element_blank()
  )
```

Facet by region
PCV = additively patterned between, but still need to look at within it 
Calculate VPC
depression MAIHDA faceted their visualizations

Since that 18-24 group is so high, I wonder if we should look at prevalence of tobacco free policies on campuses as another aspect… will regions with less policies see higher use? I don’t know enough about the effectiveness of those policies to reduce smoking among young people so maybe that’s too far of a stretch.

color-code age
Change factor levels
1-2 min about dataset & regions
hype team for MAIHDA & why it's better
policy & implications
ACES framework

predicted probabilities
prevalence rates 

