---
title: "Graphs"
author: "Lauren Berny"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(rio)
library(tidyverse)
library(psych)

```


# Load Estimates

```{r}
wv4_est_weighted <- readRDS(here("models", "Wave 4", 
                                 "Weighted Bayesian", "wv4_weighted_est.RDS"))
wv7_est_weighted <- readRDS(here("models", "Wave 7", 
                                 "Weighted Bayesian", "wv7_weighted_est.RDS"))
obs_wv4_weighted <- readRDS(here("models", "Wave 4", 
                                 "Weighted Bayesian", "obs_wv4_weighted.RDS"))
obs_wv7_weighted <- readRDS(here("models", "Wave 7", 
                                 "Weighted Bayesian", "obs_wv7_weighted.RDS"))
```


# Data Prep

```{r}
# Wave 4
wv4_est_weighted <- left_join(wv4_est_weighted, obs_wv4_weighted, by = "strata")

wv4_est_weighted <- wv4_est_weighted %>% 
 mutate(wave = 4) %>% 
 mutate(est_obs_dif = eprod_edsd - mean) %>% 
 mutate(mean = mean*100,
        q5 = q5*100,
        q95 = q95*100,
        eprod_edsd = eprod_edsd*100,
        est_obs_dif = est_obs_dif*100)

# Wave 7
wv7_est_weighted <- left_join(wv7_est_weighted, obs_wv7_weighted, by = "strata")

wv7_est_weighted <- wv7_est_weighted %>% 
 mutate(wave = 7) %>% 
 mutate(est_obs_dif = eprod_edsd - mean) %>% 
 mutate(mean = mean*100,
        q5 = q5*100,
        q95 = q95*100,
        eprod_edsd = eprod_edsd*100,
        est_obs_dif = est_obs_dif*100)

# Dataframe with both waves, rows
est_weighted <- rbind.data.frame(wv4_est_weighted, wv7_est_weighted)

# Dataframe with both waves, columns
est_weighted_wide <- est_weighted %>%
  pivot_wider(
    id_cols = c(strata, strata_label),
    names_from = wave,
    values_from = c(mean, q5, q95, eprod_edsd),
    names_glue = "{.value}_wave{wave}") %>% 
 mutate(est_wave_diff = mean_wave7-mean_wave4)
```

# Wave 4: Weighted Estimates

## Etimates graph

```{r}
wv4_est_weighted %>%
 ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum Rank") +
  coord_flip() +
  theme_bw()
```

### Faceted by region

```{r}
wv4_est_weighted %>%
  mutate(region = word(strata_label, 1, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ region, scales = "free_y", ncol = 1)
```

### Faceted by race/ethnicity

```{r}
wv4_est_weighted %>%
  mutate(race_ethnicity = word(strata_label, 2, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ race_ethnicity, scales = "free_y", ncol = 1)
```

### Faceted by sex

```{r}
wv4_est_weighted %>%
  mutate(sex = word(strata_label, 3, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ sex, scales = "free_y", ncol = 1)
```

### Faceted by age

```{r}
wv4_est_weighted %>%
  mutate(age = word(strata_label, 4, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ age, scales = "free_y", ncol = 1)
```

## Estimated vs. observed graph

On average, the mean predicted EDSD rate was only 0.14 percentage points low than the weighted, observed rate (5.33% vs. 5.47%). 


```{r}
wv4_est_weighted %>%
  ggplot(aes(x = reorder(strata_label, abs(est_obs_dif)))) +
  geom_point(aes(y = mean, color = "Predicted"), size = 2) +
  geom_point(aes(y = eprod_edsd, color = "Observed"), size = 2) +
  scale_color_manual(values = c("Predicted" = "black", "Observed" = "purple")) +
  ylab("Percent EDSD E-Product Use") +
  xlab("Stratum (Ranked by Accuracy, Lowest to Highest)") +
  coord_flip() +
  theme_bw() +
  theme(legend.title = element_blank())

describe(wv4_est_weighted$eprod_edsd)
describe(wv4_est_weighted$mean)
```

# Wave 7: Weighted Estimates

## Full

```{r}
wv7_est_weighted %>%
 ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted Percent EDSD E-Product User") +
  xlab("Stratum Rank") +
  coord_flip() +
  theme_bw()
```



### Faceted by region

```{r}
wv7_est_weighted %>%
  mutate(region = word(strata_label, 1, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted Percent EDSD E-Product User") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ region, scales = "free_y", ncol = 1)
```

### Faceted by race/ethnicity

```{r}
wv7_est_weighted %>%
  mutate(race_ethnicity = word(strata_label, 2, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted Percent EDSD E-Product User") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ race_ethnicity, scales = "free_y", ncol = 1)
```

### Faceted by sex

```{r}
wv7_est_weighted %>%
  mutate(sex = word(strata_label, 3, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted Percent EDSD E-Product User") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ sex, scales = "free_y", ncol = 1)
```

### Faceted by age

```{r}
wv7_est_weighted %>%
  mutate(age = word(strata_label, 4, sep = fixed(","))) %>% 
  ggplot(aes(y = mean, x = reorder(strata_label, mean))) +
  geom_pointrange(aes(ymin = q5, ymax = q95)) +
  ylab("Predicted Percent EDSD E-Product User") +
  xlab("Stratum") +
  coord_flip() +
  theme_bw() +
  facet_wrap(~ age, scales = "free_y", ncol = 1)
```


## Estimated vs. observed graph

On average, the mean predicted EDSD rate was only 0.17 percentage points higher than the weighted, observed rate (9.67% vs. 9.5%). 

```{r}
wv7_est_weighted %>%
  ggplot(aes(x = reorder(strata_label, abs(est_obs_dif)))) +
  geom_point(aes(y = mean, color = "Predicted"), size = 2) +
  geom_point(aes(y = eprod_edsd, color = "Observed"), size = 2) +
  scale_color_manual(values = c("Predicted" = "black", "Observed" = "purple")) +
  ylab("Predicted EDSD E-Product Use Rates") +
  xlab("Stratum (Ranked by Accuracy, Lowest to Highest)") +
  coord_flip() +
  theme_bw() +
  theme(legend.title = element_blank())

describe(wv7_est_weighted$eprod_edsd)
describe(wv7_est_weighted$mean)
```

# Wave 4 vs. Wave 7 Estimates

```{r}
est_weighted_wide %>%
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  
  # Wave 4 point + interval
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +

  # Wave 7 point + interval
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +

  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted E-Product Use (95% Crl)") +
  xlab("Strata") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
```


## Highlight strata with decreased use

```{r}
est_weighted_wide %>%
  mutate(wave4_color_group = ifelse(est_wave_diff < 0, "Wave 4", "Gray"),
         wave7_color_group = ifelse(est_wave_diff < 0, "Wave 7", "Gray")) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +

   # Wave 4 point + interval
  geom_point(aes(y = mean_wave4, color = wave4_color_group), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4, color = wave4_color_group)) +

  # Wave 7 point + interval
  geom_point(aes(y = mean_wave7, color = wave7_color_group), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7, color = wave7_color_group)) +

  # Custom colors for each group
  scale_color_manual(values = c(
    "Wave 4" = "#206997",  # Blue
    "Wave 7" = "#7db63b",  # Green
    "Gray" = "gray70"
  )) +

  ylab("Predicted E-Product Use (95% Crl)") +
  xlab("Strata") +
  theme_bw() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 90, hjust = 1, size = 8)
  )
```



## Faceted by region

```{r}
region_facet <- est_weighted_wide %>%
  mutate(region = word(strata_label, 1, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ region, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())

region_facet
```


## Faceted by race/ethnicity

```{r}
est_weighted_wide %>%
  mutate(race_ethnicity = word(strata_label, 2, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ race_ethnicity, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())
```


## Faceted by sex - version 1

```{r}
# Split the label by comma
parts <- strsplit(est_weighted_wide$strata_label, ",\\s*")

# Create new label excluding the 3rd element (sex)
est_weighted_wide$lab <- sapply(parts, function(x) paste(x[-3], collapse = ", "))


est_weighted_wide %>%
  mutate(sex = word(strata_label, 3, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(lab, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted E-Product Use (95% Crl)") +
  xlab("Strata") +
  coord_flip() +
  facet_wrap(~ sex, scales = "free_y", ncol = 2) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 7),
        strip.text = element_text(size = 11, face = "bold"))
```

## Faceted by sex - version 2

```{r}
# Split the label by comma
parts <- strsplit(est_weighted_wide$strata_label, ",\\s*")

# Create new label excluding the 3rd element (sex)
est_weighted_wide$lab <- sapply(parts, function(x) paste(x[-3], collapse = ", "))

est_weighted_wide %>%
  mutate(sex = word(strata_label, 3, sep = fixed(","))) %>% 
  group_by(sex) %>%
  slice_max(order_by = est_wave_diff, n = 15, with_ties = FALSE) %>%
  ungroup() %>%
  ggplot(aes(x = reorder(lab, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted E-Product Use (95% Crl)") +
  xlab("Strata") +
  coord_flip() +
  facet_wrap(~ sex, scales = "free_y", ncol = 2) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 7),
        strip.text = element_text(size = 11, face = "bold"))

```

## Faceted by sex - version 3

```{r}
# Split the label by comma
parts <- strsplit(est_weighted_wide$strata_label, ",\\s*")

# Create new label excluding the 3rd element (sex)
est_weighted_wide$lab <- sapply(parts, function(x) paste(x[-3], collapse = ", "))

# Define your desired region order
region_levels <- c("West", "South", "Northeast", "Midwest")  # or your custom order

regionsexgrouped <- est_weighted_wide %>%
  mutate(
    sex = word(strata_label, 3, sep = fixed(",")),
    region = word(strata_label, 1, sep = fixed(",")),
    race = word(strata_label, 2, sep = fixed(",")),
    age = word(strata_label, 4, sep = fixed(",")),
    
    region = factor(region, levels = region_levels),            # enforce region order
    region_order = as.numeric(region),                          # numeric for sorting
    
    lab = paste(region, race, age, sep = ", "),
    
    # Create a combined sort key: region order + est_wave_diff
    lab = fct_reorder(lab, region_order * 100 + est_wave_diff)  # multiply to give region more weight
  ) %>%
  ggplot(aes(x = lab)) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted E-Product Use (95% CrI)") +
  xlab("Strata") +
  coord_flip() +
  facet_wrap(~ sex, scales = "free_y", ncol = 2) +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(size = 7),
        strip.text = element_text(size = 11, face = "bold"))

```


## Faceted by age

```{r fig.width=8, fig.height=12}
age_facet <- est_weighted_wide %>%
  mutate(age = word(strata_label, 4, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ age, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())

age_facet
```

## Faceted by Age and Sex

```{r}
age_sex_facet <- est_weighted_wide %>%
  mutate(age = word(strata_label, 4, sep = fixed(",")),
         sex = word(strata_label, 3, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "#206997") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "#7db63b") +
  scale_color_manual(values = c("Wave 4" = "#206997", "Wave 7" = "#7db63b")) +
  ylab("Predicted E-Product Use (95% Crl)") +
  xlab("Stratum") +
  coord_flip() +
  facet_wrap(~ interaction(age, sex), scales = "free_y") +
  theme_bw() +
  theme(legend.title = element_blank(),
        strip.text = element_text(size = 11, face = "bold"))

age_sex_facet
```


# Catepillar Plots

# Wave 4

## Full Strata

```{r}
wv4_est_weighted %>% 
 ggplot(aes(x = mean, y = reorder(strata_label, mean))) +
  geom_point(size = 2, color = "#007030") +
  geom_errorbarh(aes(xmin = q5, xmax = q95), height = 0.0, color = "#007030") +
  labs(
    x = "Predicted E-Product Use (95% Crl)",
    y = "Strata"
  ) +
 coord_flip() +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
```

## Top 30

```{r}
wv4_est_weighted %>% 
 arrange(desc(mean)) %>% 
 slice_head(n=30) %>% 
 ggplot(aes(x = mean, y = reorder(strata_label, mean))) +
  geom_point(size = 2, color = "#007030") +
  geom_errorbarh(aes(xmin = q5, xmax = q95), height = 0.0, color = "#007030") +
  labs(
    x = "Predicted E-Product Use (95% Crl)",
    y = "Strata"
  ) +
 coord_flip() +
 xlim(c(0,20)) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10))
```

## Top 15

```{r}
wv4_est_weighted %>% 
 arrange(desc(mean)) %>% 
 slice_head(n=15) %>% 
 ggplot(aes(x = mean, y = reorder(strata_label, mean))) +
  geom_point(size = 2, color = "#007030") +
  geom_errorbarh(aes(xmin = q5, xmax = q95), height = 0.0, color = "#007030") +
  labs(
    x = "Predicted E-Product Use (95% Crl)",
    y = "Strata"
  ) +
 coord_flip() +
 xlim(c(0,20)) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10))
```


# Catepillar Plots

# Wave 7

## Full Strata

```{r}
wv7_est_weighted %>% 
 ggplot(aes(x = mean, y = reorder(strata_label, mean))) +
  geom_point(size = 2, color = "#007030") +
  geom_errorbarh(aes(xmin = q5, xmax = q95), height = 0.0, color = "#007030") +
  labs(
    x = "Predicted E-Product Use (95% Crl)",
    y = "Strata"
  ) +
 coord_flip() +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 8))
```

## Top 15

```{r}
wv7_est_weighted %>% 
 arrange(desc(mean)) %>% 
 slice_head(n=15) %>% 
 ggplot(aes(x = mean, y = reorder(strata_label, mean))) +
  geom_point(size = 2, color = "#007030") +
  geom_errorbarh(aes(xmin = q5, xmax = q95), height = 0.0, color = "#007030") +
  labs(
    x = "Predicted E-Product Use (95% Crl)",
    y = "Strata"
  ) +
 coord_flip() +
 xlim(c(0,30)) +
  theme_minimal() +
 theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10))
```