---
title: "Design-Weighted MAIHDA Results"
author: "Lauren Berny"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(rio)
library(tidyverse)
library(psych)

wave4_nullmod <- readRDS(here("models", "Wave 4", "Weighted Bayesian", "wave4_nullmod.RDS"))
wave4_fullmod <- readRDS(here("models", "Wave 4", "Weighted Bayesian", "wave4_fullmod.RDS"))
wave7_nullmod <- readRDS(here("models", "Wave 7", "Weighted Bayesian", "wave7_nullmod.RDS"))
wave7_fullmod <- readRDS(here("models", "Wave 7", "Weighted Bayesian", "wave7_fullmod.RDS"))
source(here("scripts", "helpers.R"))
est_weighted_wide <- readRDS(here("scripts", "est_weighted_wide.RDS"))

```


# Model Summaries

## Wave 4

```{r}
wave4_full_stan <- wave4_fullmod$stan_fit

wave4_full_sum = as.data.frame(rstan::summary(wave4_fullmod$stan_fit,
                                probs = c(0.025, 0.975))$summary)


wave4_full_estimates <- wave4_full_sum %>% 
  filter(rownames(.) %in% c("b[1]", "b[2]", "b[3]", 
                            "b[4]", "b[5]", "b[6]",
                            "b[7]", "b[8]", "b[9]",
                            "b_Intercept")) %>% 
  mutate(
    parameter = c("Northeast",
                  "South",
                  "West",
                  "Age_25-44",
                  "Age_45+",
                  "Male",
                  "Hispanic",
                  "Other",
                  "White",
                  "Intercept"),
    OR = format(round(exp(mean),digits=2),nsmall=2),
    LB = format(round(exp(`2.5%`),digits=2),nsmall=2),
    UB = format(round(exp(`97.5%`),digits=2),nsmall=2),
    est = paste(OR," (",LB,", ",UB,")", sep="")) %>% 
 dplyr::select(parameter, OR, LB, UB, est)

wave4_full_estimates
```

## Wave 7

```{r}
wave7_full_stan <- wave7_fullmod$stan_fit

wave7_full_sum = as.data.frame(rstan::summary(wave7_fullmod$stan_fit,
                                probs = c(0.025, 0.975))$summary)


wave7_full_estimates <- wave7_full_sum %>% 
  filter(rownames(.) %in% c("b[1]", "b[2]", "b[3]", 
                            "b[4]", "b[5]", "b[6]",
                            "b[7]", "b[8]", "b[9]",
                            "b_Intercept")) %>% 
  mutate(
    parameter = c("Northeast",
                  "South",
                  "West",
                  "Age_25-44",
                  "Age_45+",
                  "Male",
                  "Hispanic",
                  "Other",
                  "White",
                  "Intercept"),
    OR = format(round(exp(mean),digits=2),nsmall=2),
    LB = format(round(exp(`2.5%`),digits=2),nsmall=2),
    UB = format(round(exp(`97.5%`),digits=2),nsmall=2),
    est = paste(OR," (",LB,", ",UB,")", sep="")) %>% 
 dplyr::select(parameter, OR, LB, UB, est)

wave7_full_estimates
```


# MAIHDA

## Wave 4

Approximately 11.67% of between group differences in e-product use were attributable to interaction effects, providing evidence of heterogeneity of intersectional estimates around average main effects.

```{r}
modlist_wv4 <- list(wave4_nullmod[["stan_fit"]], wave4_fullmod[["stan_fit"]])

variance(modlist_wv4)
```

## Wave 7

Approximately 7.59% of between group differences in e-product use were attributable to interaction effects, providing evidence of heterogeneity of intersectional estimates around average main effects.

```{r}
modlist_wv7 <- list(wave7_nullmod[["stan_fit"]], wave7_fullmod[["stan_fit"]])

variance(modlist_wv7)
```


# Group Estimates

The largest increase between waves generally appears to be stratas of Females aged 18-24. This matches with observered rates as well. Note: EDSD is "everyday/someday" e-product use.

```{r fig.height=14, fig.width=10}
est_weighted_wide %>%
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  
  # Wave 4 point + interval
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "turquoise4") +

  # Wave 7 point + interval
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "darkorchid4") +

  scale_color_manual(values = c("Wave 4" = "turquoise4", "Wave 7" = "darkorchid4")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  theme_bw() +
  theme(legend.title = element_blank())
```


```{r fig.height=14, fig.width=10}
est_weighted_wide %>%
  mutate(region = word(strata_label, 1, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "turquoise4") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "darkorchid4") +
  scale_color_manual(values = c("Wave 4" = "turquoise4", "Wave 7" = "darkorchid4")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ region, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())
```


```{r fig.height=14, fig.width=10}
est_weighted_wide %>%
  mutate(race_ethnicity = word(strata_label, 2, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "turquoise4") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "darkorchid4") +
  scale_color_manual(values = c("Wave 4" = "turquoise4", "Wave 7" = "darkorchid4")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ race_ethnicity, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())
```


```{r fig.height=14, fig.width=10}
est_weighted_wide %>%
  mutate(sex = word(strata_label, 3, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "turquoise4") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "darkorchid4") +
  scale_color_manual(values = c("Wave 4" = "turquoise4", "Wave 7" = "darkorchid4")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ sex, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())
```


```{r fig.height=14, fig.width=10}
est_weighted_wide %>%
  mutate(age = word(strata_label, 4, sep = fixed(","))) %>% 
  ggplot(aes(x = reorder(strata_label, est_wave_diff))) +
  geom_point(aes(y = mean_wave4, color = "Wave 4"), size = 2) +
  geom_pointrange(aes(y = mean_wave4, ymin = q5_wave4, ymax = q95_wave4), color = "turquoise4") +
  geom_point(aes(y = mean_wave7, color = "Wave 7"), size = 2) +
  geom_pointrange(aes(y = mean_wave7, ymin = q5_wave7, ymax = q95_wave7), color = "darkorchid4") +
  scale_color_manual(values = c("Wave 4" = "turquoise4", "Wave 7" = "darkorchid4")) +
  ylab("Predicted EDSD E-Product Use (95% Crl)") +
  xlab("Stratum (Ranked by Change, Greatest to Least)") +
  coord_flip() +
  facet_wrap(~ age, scales = "free_y", ncol = 1) +
  theme_bw() +
  theme(legend.title = element_blank())
```