---
title: "Unweighted Bayesian Models"
author: "Lauren Berny"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(brms)
library(cmdstanr)
library(dplyr)
library(marginaleffects)
library(here)

# Note: I had to install cmdStan - ran install_cmdstan() after loading cmdstanr; 
# if needed cmdstanr is downloaded via github remotes::install_github("stan-dev/cmdstanr")
```

# Load Data

```{r}
load(here("data", "combined_clean.RData"))
```


# Narrow to Analytic Samples

```{r}
# Wave 4

dat_wv4 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==4) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv4 <- dat_wv4 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

n_distinct(dat_wv4$strata)

# Wave 7

dat_wv7 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv7 <- dat_wv7 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

n_distinct(dat_wv7$strata)
```

# Null Models

## Define priors

```{r}
null_priors <- c(
  # logit scale
  prior(normal(0, 2), class = Intercept),
  # variance components
  prior(inv_gamma(2, 2), class = sd))
```


## Wave 4


```{r}
set.seed(828) 

pyMDE_m1_unweighted <- 
  brm(as.factor(eprod_edsd) ~ 1 + (1 | strata),
      data = dat_wv4,
      family = bernoulli(link="logit"),
      prior = null_priors,
      chains = 4,
      iter = 8000,
      warmup = 4000,
      thin = 1,
      threads = threading(2),
      cores = 4,
      backend = "cmdstanr")
# save the model
saveRDS(pyMDE_m1_unweighted, 
        "wave4_nullmod_unweighted.rds")

```



## Wave 7

```{r}
set.seed(828) 

pyMDE_m3_unweighted <- 
  brm(as.factor(eprod_edsd) ~ 1 + (1 | strata),
      data = dat_wv7,
      family = bernoulli(link="logit"),
      prior = null_priors,
      chains = 4,
      iter = 8000,
      warmup = 4000,
      thin = 1,
      threads = threading(2),
      cores = 4,
      backend = "cmdstanr")
# save the model
saveRDS(pyMDE_m3_unweighted, 
        "wave7_nullmod_unweighted.rds")
```


# Full Models

## Define priors

```{r}
full_priors <- c(
  # logit scale
  prior(normal(0, 2), class = Intercept),
  prior(normal(0, 2), class = b),
  # variance component
  prior(inv_gamma(2, 2), class = sd))
```


## Wave 4


```{r}
set.seed(828) 

pyMDE_m2_unweighted <- 
  brm(as.factor(eprod_edsd) ~ 1 + region + age + sex + race_ethnicity + (1 | strata),
      data = dat_wv4,
      family = bernoulli(link="logit"),
      prior = full_priors,
      chains = 4,
      iter = 8000,
      warmup = 4000,
      thin = 1,
      threads = threading(2),
      cores = 4,
      backend = "cmdstanr")
# save the model
saveRDS(pyMDE_m2_unweighted, 
        "wave4_fullmod_unweighted.rds")
```
###################################################
######## !!!! OLD CODE !!!! ############
######## !!!! SEE FINAL ANALYSIS CODE !!!! ########
###################################################

## Wave 7

```{r}
set.seed(828) 

pyMDE_m4_unweighted <- 
  brm(as.factor(eprod_edsd) ~ 1 + region + age + sex + race_ethnicity + (1 | strata),
      data = dat_wv7,
      family = bernoulli(link="logit"),
      prior = full_priors,
      chains = 4,
      iter = 8000,
      warmup = 4000,
      thin = 1,
      threads = threading(2),
      cores = 4,
      backend = "cmdstanr")
# save the model
saveRDS(pyMDE_m4_unweighted, 
        "wave7_fullmod_unweighted.rds")

```


# Predictions and Stuff

## Load data

```{r}
pyMDE_m2_unweighted <- readRDS(here("models", "Wave 4", "Unweighted Bayesian", "wave4_fullmod_unweighted.RDS"))
pyMDE_m4_unweighted <- readRDS(here("models", "Wave 7", "Unweighted Bayesian", "wave7_fullmod_unweighted.RDS"))
load(here("data", "combined_clean.RData"))
```


## Wave 7

### Predictions for strata

#### Method 1

**For intercept-only model per strata, "Raw" strata effects**

**What it does:**
Uses only the intercept:
Fixed-effect intercept (global_intercept)
Strata-specific random intercept (ranef_estimate)
Ignores all covariates (region, age, sex, race_ethnicity)

**Useful for:**
Getting a baseline predicted probability per strata
Captures between-strata variation without adjusting for covariates

**Not accounting for:**
Differences in covariate distributions across strata
Any predictors in the fixed-effect part of the model

```{r}
# 1. Extract random intercept estimates for strata
ranef_vals <- ranef(pyMDE_m4_unweighted)$strata
strata_estimates <- ranef_vals[, "Estimate", "Intercept"]

# 2. Get the global (fixed) intercept
fixef_vals <- fixef(pyMDE_m4_unweighted)
global_intercept <- fixef_vals["Intercept", "Estimate"]

# 3. Combine to get the linear predictor and predicted probability
strata_probs <- data.frame(
  strata = rownames(ranef_vals),
  ranef_estimate = strata_estimates,
  linear_predictor = strata_estimates + global_intercept,
  predicted_prob = plogis(strata_estimates + global_intercept)
)
```

#### Method 2

**For full model adjusted per strata covariates, Model’s expected % EDSD use for that strata’s profile**

**Computes predicted probabilities using:**
All fixed effects (region, age, sex, etc.)
The random intercept for each strata (re_formula = NULL)
newdata_strata includes 1 row per strata, but includes the covariates

**Useful for:**
Estimating adjusted probabilities per strata, reflecting the model’s fixed effects
Showing what the model expects for each strata given its covariate values

**Depends on:**
The actual covariates used for each strata in newdata_strata
May smooth over strata-level differences if covariates explain a lot

```{r}
dat_wv7 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv7 <- dat_wv7 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

newdata_strata <- dat_wv7 %>%
 dplyr::select(strata, region, age, sex, race_ethnicity) %>% 
 unique()

preds <- fitted(pyMDE_m4_unweighted,
                newdata = newdata_strata,
                re_formula = NULL,  # include random effects
                summary = TRUE)     # get mean and CI

preds_df <- as.data.frame(preds)

strata_preds <- cbind.data.frame(newdata_strata, preds_df)

strata_preds <- strata_preds %>% 
 mutate(strata_label = paste(region, race_ethnicity, sex, age, sep = ", "))
```

### Graphs for second version of preds

```{r}
strata_preds %>% 
 ggplot(aes(y = Estimate, x = reorder(strata_label, Estimate))) +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.2, color = "black") +  # Black error bars
  geom_point(shape = 21, fill = "purple3", color = "black", size = 2) +  # Colored points
  ylab("Predicted Percent EDSD E−Product User, Model 2 for Wave 7") +
  xlab("Strata") +
  coord_flip() +
  theme_bw()

observed_strata_percents <- dat_wv7 %>%
  group_by(strata) %>%
  summarise(
    percent_using = mean(eprod_edsd, na.rm = TRUE) * 100,
    n = n()
  ) %>%
  ungroup()

 
compare_preds_obs <- left_join(strata_preds, observed_strata_percents, by = "strata")

compare_preds_obs %>% 
 mutate(diff = (Estimate*100) - percent_using) %>% 
 arrange(desc(abs(diff)))
```




## Wave 4


### Strata Preds

Used second version for calculating preds.

```{r}
dat_wv4 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==4) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv4 <- dat_wv4 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

newdata_strata4 <- dat_wv4 %>%
 dplyr::select(strata, region, age, sex, race_ethnicity) %>% 
 unique()

preds_4 <- fitted(pyMDE_m2_unweighted,
                newdata = newdata_strata4,
                re_formula = NULL,  # include random effects
                summary = TRUE)     # get mean and CI

preds_df4 <- as.data.frame(preds_4)

strata_preds4 <- cbind.data.frame(newdata_strata4, preds_df4)

strata_preds4 <- strata_preds4 %>% 
 mutate(strata_label = paste(region, race_ethnicity, sex, age, sep = ", "))
```

### Graphs for Second Version of Preds

```{r}
strata_preds4 %>% 
 ggplot(aes(y = Estimate, x = reorder(strata_label, Estimate))) +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.2, color = "black") +  # Black error bars
  geom_point(shape = 21, fill = "purple3", color = "black", size = 2) +  # Colored points
  ylab("Predicted Percent EDSD E−Product User, Model 2 for Wave 7") +
  xlab("Strata") +
  coord_flip() +
  theme_bw()


observed_strata_percents4 <- dat_wv4 %>%
  group_by(strata) %>%
  summarise(
    percent_using = mean(eprod_edsd, na.rm = TRUE) * 100,
    n = n()
  ) %>%
  ungroup()

 
compare_preds_obs4 <- left_join(strata_preds4, observed_strata_percents4, by = "strata")

compare_preds_obs4 %>% 
 mutate(diff = (Estimate*100) - percent_using) %>% 
 arrange(desc(abs(diff)))
```
