---
title: 'Wave 7: Bayesian Analyses'
author: "Lauren Berny"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(csSampling)
library(dplyr)
library(brms)
library(rstan)
library(survey)
library(cmdstanr)
library(tidyverse)
library(ggeffects)
library(lme4)
library(merTools)
library(labelled)
library(sjPlot)
library(Metrics)
library(janitor)
library(here)
library(rio)
library(posterior)
library(tibble)
library(purrr)
library(survey)
library(gtsummary)
library(cardx)
```

# Load Wave 7 Data

```{r cars}
wave7_nullmod <- readRDS(here("models", "Wave 7", "Weighted Bayesian", "wave7_nullmod.RDS"))
wave7_fullmod <- readRDS(here("models", "Wave 7", "Weighted Bayesian", "wave7_fullmod.RDS"))
wave7_nullmod_uw <- readRDS(here("models", "Wave 7", "Unweighted Bayesian", "wave7_nullmod_unweighted.RDS"))
wave7_fullmod_uw <- readRDS(here("models", "Wave 7", "UnWeighted Bayesian", "wave7_fullmod_unweighted.RDS"))
source(here("scripts", "helpers.R"))
load(here("data", "combined_clean.RData"))
```

# Make Labels

```{r}
labs <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

labs <- labs %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

# n_distinct(groups$strata)

labs <- labs %>%
  mutate(strata_label = paste(region, race_ethnicity, sex, age, sep = ", ")) %>%
  dplyr::select(strata, strata_label) %>% 
  unique() %>% 
  arrange(strata) %>%
  mutate(strata_rank = row_number()) %>% 
  mutate(variable = paste0("strata_", strata_rank)) %>% 
  dplyr::select(-strata_rank)
```

# Summary of Results

Summary adapted from NSDUH depression paper.

## Wave 7 full and weighted

```{r}
wave7_full_stan <- wave7_fullmod$stan_fit

## Extract parameter estimates, effective sample size (ESS), and r-hat 
## from each model fit. Specify 95% credible intervals.


wave7_full_sum = as.data.frame(rstan::summary(wave7_fullmod$stan_fit,
                                probs = c(0.025, 0.975))$summary)


wave7_full_estimates <- wave7_full_sum %>% 
  # keep rows with beta coefficients
  # 10/24/2024 Note: We have updated this to the correct intercept parameter 
  # ("b_Intercept")
  filter(rownames(.) %in% c("b[1]", "b[2]", "b[3]", 
                            "b[4]", "b[5]", "b[6]",
                            "b[7]", "b[8]", "b[9]",
                            "b_Intercept")) %>% 
  mutate(
    parameter = c("Northeast",
                  "South",
                  "West",
                  "Age_25-44",
                  "Age_45+",
                  "Male",
                  "Hispanic",
                  "Other",
                  "White",
                  "Intercept"),
    OR = format(round(exp(mean),digits=2),nsmall=2),
    LB = format(round(exp(`2.5%`),digits=2),nsmall=2),
    UB = format(round(exp(`97.5%`),digits=2),nsmall=2),
    est = paste(OR," (",LB,", ",UB,")", sep="")) %>% 
 dplyr::select(parameter, OR, LB, UB, est)

wave7_full_estimates
```

## Wave 7 full and unweighted

```{r}
wave7_full_sum_uw <- summary(wave7_fullmod_uw)

wave7_full_sum_uw <- wave7_full_sum_uw[["fixed"]]

wave7_full_sum_uw %>% 
  dplyr::select(Estimate, `l-95% CI`, `u-95% CI`) %>% 
  mutate(
    OR = format(round(exp(Estimate),digits=2),nsmall=2),
    LB = format(round(exp(`l-95% CI`),digits=2),nsmall=2),
    UB = format(round(exp(`u-95% CI`),digits=2),nsmall=2),
    est = paste(OR," (",LB,", ",UB,")", sep="")) %>% 
 dplyr::select(OR, LB, UB, est) %>% 
 slice(c(2:n(), 1))
```


# MAIHDA: PCV/VPC

## Weighted

```{r}
modlist_wv7 <- list(wave7_nullmod[["stan_fit"]], wave7_fullmod[["stan_fit"]])

variance(modlist_wv7)
```


# Strata Estimates for Wave 7

## Weighted

### Extract posterior draws

```{r warning=FALSE}
posterior <- as_draws_df(wave7_fullmod[["stan_fit"]])

# Fixed effects matrix: one row per draw, one column per beta
beta_matrix <- posterior %>%
  dplyr::select(starts_with("b[")) %>%
  as.matrix()  # dimension: [n_draws x k]

# Global intercept
intercept_vector <- posterior$b_Intercept  # length = n_draws

# Random intercepts per strata (r_1_1[1] to r_1_1[96])
random_intercepts_matrix <- posterior %>%
  dplyr::select(matches("^r_1_1\\[[0-9]+\\]$")) %>%
  as.matrix()  # dimension: [n_draws x 96]
```

### Create design matrix of covariate values for each strata

```{r}
# 2. Create 1 row per strata with typical covariates

dat_wv7 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv7 <- dat_wv7 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

newdata_strata <- dat_wv7 %>%
 dplyr::select(strata, region, age, sex, race_ethnicity) %>% 
 arrange(strata) %>% ## THIS IS ESSENTIAL FOR ORDER TO BE CORRECT ACROSS ALL MATRICES
 unique()

rownames(newdata_strata) <- NULL

# 3. Create the design matrix X using the same formula

# Create model matrix WITHOUT intercept (b_Intercept handled separately)
X <- model.matrix(~ region + age + sex + race_ethnicity, data = newdata_strata)

X_covariates <- X[, 2:10]
```


### Create predicted probabilities per strata

These are **total effects**, i.e., intercept + random intercept + fixed effects.

```{r}
# Ensure covariates are in correct matrix format: [96 strata x k covariates]
X_covariates <- as.matrix(X_covariates)  # 96 x k

# Function to compute predicted probabilities for one strata
compute_strata_probs <- function(stratum_index) {
  # Covariate row for that strata (1 x k)
  x_row <- X_covariates[stratum_index, , drop = FALSE]
  
  # Multiply covariates by fixed effects per draw: [n_draws x k] * [k x 1] = [n_draws x 1]
  xb <- beta_matrix %*% t(x_row)  # [n_draws x 1]
  
  # Linear predictor: intercept + random intercept + fixed effects
  linpred <- intercept_vector + random_intercepts_matrix[, stratum_index] + xb[, 1]
  
  # Convert to probability
  plogis(linpred)
}

# Compute probabilities for all 96 strata
strata_probs_list <- map(1:96, compute_strata_probs)

# Combine into a data frame: rows = draws, columns = strata
strata_probs_matrix <- do.call(cbind, strata_probs_list)
colnames(strata_probs_matrix) <- paste0("strata_", 1:96)
```

### Posterior summaries for each strata across 16k draws

```{r}
# Get posterior summaries per strata (mean, SD, 95% CI)
posteriorsum_weighted <- posterior::summarise_draws(strata_probs_matrix)

posteriorsum_weighted <- left_join(labs, posteriorsum_weighted, by = "variable")

wv7_weighted_est <- posteriorsum_weighted %>% 
 arrange(mean)

wv7_weighted_est

# saveRDS(wv7_weighted_est, "wv7_weighted_est.RDS")
```


## Unweighted

**Anwesha/Janette/Elizabeth** -- I think this is right but am not sure. Thoughts?

```{r}
strata_probs_uw <- fitted(
  wave7_fullmod_uw,
  newdata = newdata_strata,
  re_formula = NULL,    # argument to include fixed + random effects
  summary = TRUE,       # posterior means and intervals
  scale = "response"    # transforms logits to probabilities
)

wv7_unweighted_est <- cbind.data.frame(labs, strata_probs_uw)

wv7_unweighted_est %>% 
 arrange(Estimate)
```

# Observed Weighted Estimates

```{r}
# Step 1: Define your survey design
svy_design <- svydesign(
  id = ~var_psu,
  strata = ~var_strat,
  weights = ~weight,
  data = dat_wv7,
  nest = TRUE  # important if strata and PSU are nested (common case)
)

# Step 2: Get weighted proportion of eprod_edsd == 1 by strata
obs_wv7_weighted <- svyby(
  ~eprod_edsd,
  ~strata,  # your target grouping variable
  svy_design,
  svymean,
  vartype = "se")  # optional: include standard error and confidence intervals

# saveRDS(obs_wv7_weighted, "obs_wv7_weighted.RDS")

# Tables

tbl_svysummary(
  data = svy_design,
  include = c(region, race_ethnicity, sex, age, eprod_edsd),
  label = list(
   region ~ "U.S. Region",
   race_ethnicity ~ "Race/Ethnicity",
   sex ~ "Sex",
   age ~ "Age Group (Years)",
   eprod_edsd ~ "Every Day/Some Day Electronic Nicotine Product User"
  ),
  statistic = all_categorical() ~ "{p}%",
  percent = "column",
  digits = all_categorical() ~ 1) %>% 
 modify_caption("**Wave 7: Weighted Descriptive Statistics**") %>% 
  modify_footnote(everything() ~ NA)

```

