---
title: "Wave 7 Full Model"
author: "Waddling the Path"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(csSampling)
library(dplyr)
library(brms)
library(rstan)
library(survey)
library(cmdstanr)
library(tidyverse)
library(ggeffects)
library(lme4)
library(merTools)
library(labelled)
library(sjPlot)
library(Metrics)
library(janitor)
library(here)
library(rio)
```

# Load and Prepare Data

Must filer out any cases with missing weights, strata demos, and outcome.

```{r}

load(here("data", "combined_clean.RData"))

dat <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat <- dat %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

n_distinct(dat$strata)
```


# MAIHDA Prep

## Define priors

If we did not have any covariates (like in null model), you do not include the prior for beta.

```{r}
path_priors <- c(
  # logit scale
  prior(normal(0, 2), class = Intercept),
  prior(normal(0, 2), class = b),
  # variance component
  prior(inv_gamma(2, 2), class = sd))
```



## Survey rep object

```{r}
dat$wt_norm <- dat$weight*(length(dat$weight)/sum(dat$weight))

design_sp2 <- svrepdesign(
  data = dat,
  type = "Fay",
  rho = 0.3,
  repweights = dat[, grep("^rep_weight_[0-9]+$", names(dat))],
  weights = ~wt_norm,
  mse = TRUE)

# Check mean of weights from subpop survey design object
summary(design_sp2$pweights)
# Calibrate weights so the mean=1
design_sp2 <- calibrate(design_sp2,
                        ~ 1,
                        c(`(Intercept)` = length(design_sp2$pweights)),
                        compress = FALSE)
# Check mean after calibration
summary(design_sp2$pweights) # Mean=1
```



# MAIHDA

```{r}
# Write and save Stan file
stancode_pyMDE_m4 <- make_stancode(
  brmsformula(
    as.factor(eprod_edsd)| weights(wt_norm) ~ 
      1 + region + age + sex + race_ethnicity + (1 | strata)
    ), 
  data = dat,
  prior = path_priors,
  family = bernoulli(link="logit"),
  save_model = "brms_pyMDE_m4.stan")


# Load the Stan file
modbrms_pyMDE_m4 <- stan_model("brms_pyMDE_m4.stan")

# Set up data
databrms_pyMDE_m4 <- make_standata(
  brmsformula(
    as.factor(eprod_edsd)| weights(wt_norm) ~ 
      1 + region + age + sex + race_ethnicity + (1 | strata)
    ),
  data = design_sp2$variables,
  prior = path_priors,
  family = bernoulli(link="logit"))

# Set Stan model weights = survey design weights
databrms_pyMDE_m4$weights <- design_sp2$pweights


set.seed(828) # for reproducible results
pyMDE_m4 <- cs_sampling(
  svydes = design_sp2, # use the subpop-defined survey object
  mod_stan = modbrms_pyMDE_m4,
  data_stan = databrms_pyMDE_m4,
  ctrl_stan = list(chains = 4,
                   iter = 8000, # 16,000 total iterations (8,000 post-warmup)
                   warmup = 4000, # 8,000 warmups
                   prior = path_priors,
                   backend = "cmdstanr",
                   threads = threading(2),
                   thin = 1),
  rep_design = TRUE,
  sampling_args = list(cores = 4))

saveRDS(pyMDE_m4, file="wave7_fullmod.RDS")
```


# Post-Estimation Predictions

```{r}
wave7_fullmod <- readRDS(here("models", "Wave 7", "Weighted Bayesian", "wave7_fullmod.RDS"))
load(here("data", "combined_clean.RData"))
```

## Extract

Note: From ChatGPT, sort of got overwhelemed by the depression tutorial. Probably should work on that, though, as I am not confident how correct this is

```{r}
# 1. Extract posterior draws from the stan_fit object

# Extract posterior draws
draws <- rstan::extract(wave7_fullmod[["stan_fit"]])

# Key components
b_draws       <- draws[["b"]]           # [iterations x predictors]
b_Intercept   <- draws[["b_Intercept"]] # [iterations]
re_draws      <- draws[["r_1_1"]]       # [iterations x strata]


# 2. Create 1 row per strata with typical covariates

dat_wv7 <- full %>% 
 mutate(across(region:age, as.factor)) %>%
 filter(wave==7) %>% 
 filter(!is.na(weight)) %>% 
 filter(!is.na(sex)) %>% 
 filter(!is.na(age)) %>% 
 filter(!is.na(eprod_edsd))

dat_wv7 <- dat_wv7 %>% 
  mutate(strata = 1000 * as.numeric(region) + 
                   100 * as.numeric(age) + 
                    10 * as.numeric(sex) + 
                     1 * as.numeric(race_ethnicity))

newdata_strata <- dat_wv7 %>%
 dplyr::select(strata, region, age, sex, race_ethnicity) %>% 
 unique()

# 3. Create the design matrix X using the same formula

# Create model matrix WITHOUT intercept (b_Intercept handled separately)
X <- model.matrix(~ region + age + sex + race_ethnicity, data = newdata_strata)

X <- X[, 2:10]



# 4. Compute the predicted probabilities for each strata

n_iter <- nrow(b_draws)
n_strata <- nrow(X)

prob_matrix <- matrix(NA, nrow = n_iter, ncol = n_strata)

for (s in 1:n_strata) {
  x_stratum <- as.numeric(X[s, ])
  eta <- b_Intercept + as.vector(b_draws %*% x_stratum) + re_draws[, s]
  prob_matrix[, s] <- plogis(eta)
}


strata_preds <- data.frame(
  strata = newdata_strata$strata,
  Estimate = apply(prob_matrix, 2, mean),
  Q2.5     = apply(prob_matrix, 2, quantile, 0.025),
  Q97.5    = apply(prob_matrix, 2, quantile, 0.975)
)

```

## Graph

```{r}
library(survey)

# Step 1: Define your survey design
svy_design <- svydesign(
  id = ~var_psu,
  strata = ~var_strat,
  weights = ~weight,
  data = dat_wv7,
  nest = TRUE  # important if strata and PSU are nested (common case)
)

# Step 2: Get weighted proportion of eprod_edsd == 1 by strata
svy_props <- svyby(
  ~eprod_edsd,
  ~strata,  # your target grouping variable
  svy_design,
  svymean,
  vartype = "se")  # optional: include standard error and confidence intervals

svy_props <- svy_props

labs <- dat_wv7 %>% 
 mutate(strata_label = paste(region, race_ethnicity, sex, age, sep = ", ")) %>% 
 dplyr::select(strata, strata_label) %>% 
 unique()

svy_props <- left_join(labs, svy_props, by = "strata")

svy_props %>% 
 arrange(eprod_edsd)

compare_preds_obs <- left_join(svy_props, strata_preds, by = "strata")

compare_preds_obs %>% 
 mutate(diff = (Estimate*100) - (eprod_edsd*100)) %>% 
 arrange(desc(abs(eprod_edsd)))

compare_preds_obs %>% 
 ggplot(aes(y = Estimate, x = reorder(strata_label, Estimate))) +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5), width = 0.2, color = "black") +  # Black error bars
  geom_point(shape = 21, fill = "purple3", color = "black", size = 2) +  # Colored points
  ylab("Predicted Percent EDSD E−Product User, Model 2 for Wave 7") +
  xlab("Strata") +
  coord_flip() +
  theme_bw()
```


